\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Fix occurences of "Fig ~\ref".

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). ``Connect'' starts a connection. ``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips it.}
	\label{fig:old-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}). }
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{Some hardcoded bridges are listed alphabetically by their transport. The recommended one is obfs3.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
	\label{fig:old-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy settings screen (P2). ``Connect'' starts a connection to Tor with the interface settings.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. }
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

>>>>

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). ``Connect'' starts a connection. ``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips it.}
	\label{fig:old-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure~\ref{fig:old-bridge-help}). }
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{Some hardcoded bridges are listed alphabetically by their transport. The recommended one is obfs3.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
	\label{fig:old-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy settings screen (P2). ``Connect'' starts a connection to Tor with the interface settings.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. }
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}
